Rank Verification for Exponential Families

### 2016-06-16 verifying-winner.tex
added comments to verifying-winner.tex

We now state our main theorem: under a mild technical assumption, Procedures 1--3 described above are statistically valid, even accounting for the selection.
\begin{theorem}
Assume the model~\eqref{eqn:expfam} holds and $g\left(x\right)$ is a Schur-concave function. Then:
\begin{enumerate}
\item Procedure 1 has level $\alpha$ conditional on the best population not winning (otherwise an error is impossible).
\item Procedure 2 gives a conservative $1-\alpha$ lower confidence bound for $\theta_{[1]} - \max_{j \ne [1]} \theta_{j}$.
\item Procedure 3 is a conservative step-down procedure with familywise error rate (FWER) no larger than $\alpha$.
\end{enumerate}
\label{thm:main}
\end{theorem}

@@

\begin{lemma}
\begin{enumerate}
\item Suppose $\left(x_1, x_2, x_3, \ldots\right)$ and $\left(x_1, x_2', x_3' \ldots\right)$ are two vectors in $\RR^n$. Then
$$\left(x_1, x_2, x_3, \ldots\right) \succeq \left(x_1, x_2', x_3', \ldots\right) \text{ if and only if } \left(x_2, x_3, \ldots\right) \succeq \left(x_2', x_3', \ldots\right).$$
\item (Principle of transfer) If $x_1 > x_2$ and $t \ge 0$, then
$$\left(x_1 + t, x_2, x_3, \ldots\right) \succeq \left(x_1, x_2 + t, x_3\right).$$
If the $t \le 0$, the majorization is reversed.
\end{enumerate}
\label{lma:twoprop}
\end{lemma}

@@

\item Competing sports under Bradley--Terry model. Suppose $n$ players held a round robin tournaments with the Bradley--Terry model, where player $j$ has a score $\theta_j$, and the probability of player $j$ winning against player $k$ is
$$\frac{e^{\theta_j - \theta_k}}{1 + e^{\theta_j - \theta_k}} = \frac{e^{\left(\theta_j - \theta_k\right) / 2}}{e^{\left(\theta_j - \theta_k\right) / 2} + e^{\left(\theta_k - \theta_j\right) / 2}}.$$

Let $Y_{jk}$ be an indicator for the match between player $j$ and $k$, where we take $Y_{jk} = 1$ if $j$ beats $k$ and $Y_{jk} = 0$ if $k$ beats $j$. For symmetry, we will also adopt the convention that $Y_{jk} + Y_{kj} = 1$. Thus the joint distribution of $\left(Y_{jk}\right)_{j, k}$ is
$$p\left(\left(y_{jk}\right)_{j, k}\right) \propto \exp\left(\sum_j 2\theta_j \sum_{k \ne j} y_{jk}\right)  = \exp\left(2\theta' x\right),$$
where $x_j = \sum_{k \ne j} y_{jk}$. In other words, $x_j$ is the number of wins by player $j$.

If the individual results are masked and we only know about the net wins, then
$$p\left(x\right) \propto \exp\left(2\theta' x\right) g\left(x\right),$$
where $g\left(x\right)$ is a function that count number of possible tournament results giving the net win vector $x$. A bijection proof shows that $x$ is indeed Schur-concave.

\item Comparing the variances of different normal populations. Suppose there are $n$ normal populations with laws $N\left(\mu_j, \sigma_j^2\right)$ and $m$ independent observations from each of them. The sample variance for population $j$ can be denoted as $r_j$. By Cochran's theorem, $\left(m-1\right) r_j \sim \sigma_j^2 \chi_{m-1}^2$, and thus the joint distribution of $r$ is
\begin{align*}
r & \sim \prod_{j=1}^n \left(\frac{\left(m-1\right) r_j}{\sigma_j^2}\right)^{\left(m-3\right) / 2} e^{-\left(m-1\right) r_j / 2 \sigma_j^2} 1_{\left\{r_j > 0 \right\}} \\
& \propto \exp\left(-\frac{m-1}{2 \sigma_1^2} r_1 - \cdots - \frac{m-1}{2 \sigma_n^2} r_n\right) \prod_{j=1}^n r_j^{\left(m-3\right) / 2} 1_{\left\{r > 0\right\}}.
\end{align*}
The carrier measure is $\prod_{j=1}^n r_j^{\left(m-3\right) / 2} 1_{\left\{r > 0\right\}}$, which is Schur-concave.
\end{enumerate}

@@

\begin{proof}
Since $p_j$ are all valid $p$-values,
$$\PP_{H_{0j}}\left(p_j < \alpha\right) \le \alpha.$$
S for the union null hypothesis
$$\PP_{H_0}\left(p_* < \alpha\right) = \max_j \PP_{H_{0j}}\left(p_* < \alpha\right) \le \max_j \PP_{H_{0j}}\left(p_j < \alpha\right) \le \alpha.$$
And thus $p_*$ is a valid $p$-value for the union null hypothesis. Now if $p_j$ are all exact, then equality holds above and $p_*$ is exact as well.
\end{proof}

@@

\begin{theorem}
Assume the model~\eqref{eqn:expfam} holds and $g\left(x\right)$ is a Schur-concave function. Procedure 1 (the unadjusted pairwise test) has level $\alpha$ conditional on the best population not winning.
\label{thm:seltest}
\end{theorem}

\begin{proof}
Without loss of generality, otherwise by relabeling, we consider only the case where the winner is $1$ and the runner-up is $2$, etc., i.e.\ $X_1 \ge \cdots \ge X_n$. In this case, we will test the null hypothesis $H_{01}: \theta_1 \le \max_{j > 1} \theta_j$, which is the union of the null hypotheses $H_{01j}: \theta_1 \le \theta_j$ for $j > 1$. For each of these we can construct an exact $p$-value $p_{1j}$. Hence by \Cref{lma:union}, a test based on $p_{1*} = \max_j p_{1j}$ would be exact for $H_{01}$. Procedure 1 will perform an unadjusted pairwise test comparing $X_1$ to $X_2$. Hence it is sufficient to show that $p_{12} = p_{1*}$ and that the test based on $p_{12}$ coincides with the unadjusted pairwise test.

Following the framework in \citet{Fithian:2014ws}, we consider the selection event where the winner is $1$: $$A_1 = \left\{X_1 \ge \max_{j > 1} X_j\right\}.$$
For convenience, we let
$$D_{jk} = \frac{X_j - X_k}{2} ~~~~ \text{ and } ~~~~ M_{jk} = \frac{X_j + X_k}{2}.$$

We start by re-parametrizing to replace $X_1$ and $X_j$ with $D_{1j}$ and $M_{1j}$ and consider
\begin{equation}
\mathcal{L}_{\theta_1 - \theta_j = 0} \left(D_{1j} \middle| M_{1j}, X_{\setminus\left\{1, j\right\}}, A_1\right), \text{ where } A_1 = \left\{D_{1j} \ge \max_{k \ne 1, j} X_k - M_{1j}\right\} \cap \left\{D_{1j} \ge 0\right\}.
\label{eqn:condlaw}
\end{equation}
The conditional law in \Cref{eqn:condlaw}, in particular, is a truncated distribution
\begin{align*}
D_{1j} & \sim \exp\left(\left(\theta_1 - \theta_j\right) D_{1j} + \theta_2 X_2 + \cdots + \left(\theta_1 + \theta_j\right) M_{1j} + \cdots + \theta_n X_n \right) \\
& ~~~~~~~~ g\left(M_{ij} + D_{ij}, X_2, \ldots, M_{ij} - D_{ij}, \ldots X_n\right) 1_{A_1} \\
& \sim g\left(M_{ij} + D_{ij}, X_2, \ldots, M_{ij} - D_{ij}, \ldots X_n\right) 1_{A_1}.
\end{align*}

@@

By construction, $p_{1j}$ satisfies
$$\PP_{H_{01j}}\left(p_{1j} < \alpha \middle| M_{1j}, X_{\setminus\left\{1, j\right\}}, A_1\right) = \alpha.$$
Taking expectation on both sides gives
$$\PP_{H_{01j}}\left(p_{1j} < \alpha \middle| A_1\right) = \alpha.$$
Therefore these $p_{1j}$ are indeed valid exact $p$-values.

Without loss of generality, it is sufficient to show that $p_{12} \ge p_{13}$. In the computation of either $p$-values, $X_4, \ldots, X_n$ are all conditioned on. The first point in \Cref{lma:twoprop} says that we may assume $n = 3$ without affecting the Schur-concavity of $g$. This allows us to clean up our notation and
\begin{align*}
p_{12} & = \frac{\int_{D_{12}}^\infty g\left(M_{12} + z, M_{12} - z, X_3\right) \,dz}{\int_0^\infty g\left(M_{12} + z, M_{12} - z, X_3\right) \,dz} \\
p_{13} & = \frac{\int_{D_{13}}^\infty g\left(M_{13} + z, X_2, M_{13} - z\right) \,dz}{\int_{\max\left\{X_2 - M_{13}, 0\right\}}^\infty g\left(M_{13} + z, X_2, M_{13} - z\right) \,dz}
\end{align*}

Suppose $X_2 < M_{13}$, then we can re-parametrize the integrals above to give
\begin{align*}
p_{12} & = \frac{\int_0^\infty g\left(X_1 + z, X_2 - z, X_3\right) \,dz}{\int_0^\infty g\left(M_{12} + z, M_{12} - z, X_3\right) \,dz} \\
& = \frac{\int_0^\infty g\left(X_1 + z, X_2 - z, X_3\right) \,dz}{\int_{-D_{12}}^\infty g\left(X_1 + z, X_2 - z, X_3\right) \,dz} \\
p_{13} & = \frac{\int_0^\infty g\left(X_1 + z, X_2, X_3 - z\right) \,dz}{\int_0^\infty g\left(M_{13} + z, X_2, M_{13} - z\right) \,dz} \\
& = \frac{\int_0^\infty g\left(X_1 + z, X_2, X_3 - z\right) \,dz}{\int_{-D_{13}}^\infty g\left(X_1 + z, X_2, X_3 - z\right) \,dz}
\end{align*}
To help see the re-parametrization, each of these integrals can be thought of in terms integrals along segments and rays. For example $p_{12}$ can be represented in terms integrals $A$ and $B$ in \Cref{fig:p-value}. Specifically,
$$p_{12} = \frac{B}{A + B}$$

\begin{figure}[htbp]
\begin{center}
\begin{tikzpicture}
	\coordinate (C1) at (60:5);
	\coordinate (C2) at (300:3);
	\coordinate (A) at (60:3);
	\coordinate (B) at ($(A) + (330:3)$);
	\draw[dashed] (0, 0) -- (C1);
	\draw[dashed] (0, 0) -- (C2);
	\fill[mid_green] (0, 0) -- (C1) -- ($(C1) + (7, 0)$) -- ($(C2) + (8, 0)$) -- (C2) -- cycle;
	\node[above left] at ($(C2) + (8, 0)$) {$A_1$};
	\draw[thick] (A) -- (B) node[midway, above right] {$A$};
	\draw[thick, ->] (B) -- ++(330:5) node[midway, above right] {$B$};
	\fill (A) circle(2pt) node[above left] {$\left(M_{12}, M_{12}, X_3\right)$};
	\fill (B) circle(2pt) node[above right] {$\left(X_1, X_2, X_3\right)$};
	\draw[thick, ->] (0, 0) -- (1, 0) node[right] {\tiny $\left(1, 0, 0\right)$};
	\draw[thick, ->] (0, 0) -- (120:1) node[above] {\tiny $\left(0, 1, 0\right)$};
	\draw[thick, ->] (0, 0) -- (240:1) node[below] {\tiny $\left(0, 0, 1\right)$};
\end{tikzpicture}
\end{center}
\caption{The $p$-value $p_{12}$ can be written in terms of integral $A$ along the segment and $B$ along the ray. The diagram is drawn a level set of $x_1 + x_2 + x_3$. The green region represents the selection event $A_1$.}
\label{fig:p-value}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\begin{tikzpicture}
	\coordinate (C1) at (60:5);
	\coordinate (C2) at (300:3);
	\coordinate (A) at (60:3);
	\coordinate (B) at ($(A) + (330:3)$);
	\coordinate (C) at ($(0, 0)!(B)!(C2)$);
	\coordinate (D) at ($(A) + (150:1)$);
	\draw[dashed] (0, 0) -- (C1);
	\draw[dashed] (0, 0) -- (C2);
	\fill[mid_green] (0, 0) -- (C1) -- ($(C1) + (7, 0)$) -- ($(C2) + (8, 0)$) -- (C2) -- cycle;
	\node[above left] at ($(C2) + (8, 0)$) {$A_1$};
	\draw[thick] (A) -- (B) node[midway, above right] {$A$};
	\draw[thick, ->] (B) -- ++(330:5) node[midway, below left] {$B$};
	\fill (A) circle(2pt) node[above right] {$\left(M_{12}, M_{12}, X_3\right)$};
	\fill (B) circle(2pt) node[right] {$\left(X_1, X_2, X_3\right)$};
	\draw[thick] (C) -- (B) node[midway, below right] {$C$};
	\node[below] at (C) {$\left(M_{13}, X_2, M_{13}\right)$};
	\draw[thick, ->] (B) -- ++(30:5) node[midway, above left] {$D$};
	\fill ($(0, 0)!(B)!(C2)$) circle(2pt);
	\draw[thick, dashed] (A) -- (D) node[midway, below left] {$\tilde{A}$};
	\fill (D) circle(2pt) node[above] {$\left(M_{13}, X_2 + D_{13}, X_3\right)$};
	\draw[thick, dotted] (C) -- (D) node[midway, below, rotate=-90] {$\succeq$};
	\draw[thick, dotted] (A) -- ++(0, -3) node[midway, below, rotate=-90] {$\succeq$};
	\draw[thick, dotted] ($(B) + (30:4)$) -- ($(B) + (330:4)$) node[midway, below, rotate=-90] {$\succeq$};
\end{tikzpicture}
\end{center}
\caption{The $p$-value $p_{12}$ can be written in terms of integral $A$ along the segment and $B$ along the ray; and $p_{13}$ in terms of $C$ and $D$. $A'$ would refer to the sum of $A$ with the dashed line portion labeled as $\tilde{A}$, formally explained in \Cref{eqn:int_extension}. The majorization relation is indicated by the dotted line.}
\label{fig:compare_rays}
\end{figure}

@@

For the alternative case where $X_2 \ge M_{13}$, the segment $C$ will reach the line $x_1 = x_2$ first before it reach $x_1 = x_3$, ending at $\left(X_2, X_2, X_1 - X_2 + X_3\right)$ instead. But we can still extend $A$ by $\tilde{A}$ to $\left(X_2, X_1, X_3\right)$. The rest of the proof follows. In either cases, $p_{12} \ge p_{13}$, or in generality, $p_{12} \ge p_{1j}$ for $j > 1$. In other words, $p_{12} = p_{1*}$.

@@

The proof above holds true if the exponential family is defined on the counting measure. If ties are broken independently and randomly, the end points on the rays can be considered as ``half an atom'' if the coordinates are integers, and a ``full atom'' otherwise.

@@

\begin{theorem}
\label{thm:stoch}
$X_1 \ge X_2$ in stochastic order if and only if $\theta_1 > \theta_2$.
\end{theorem}

@@

\subsection{Multinomial Case: Connection with the Subset Selection}
\label{sec:subsetsel}

\citet{Gupta:1967wg} devises a rule to select a subset that includes the maximum $\pi_j$. In other words, if the selected subset is $J\left(X\right)$, it guarantees
$$\PP\left(\argmax_j \pi_j \in J\left(X\right)\right) \ge 1 - \alpha.$$
This is achieved by finding an integer $D$, as a function on $m$, $n$ and $\alpha$, and selecting by
$$J\left(X\right) = \left\{j: X_j \ge \max_k X_k - D\right\}.$$
It also provides the method to choose $D$. The subset selection can be modified. Inherently, the event $\left\{J\left(X\right) = \left\{1\right\}\right\}$ is the same as inferring $\pi_1$ is the largest. We thus implemented their test for this purpose.

@@

\section{By How Much?}
\label{sec:confbound}

>>>>

We now state our main theorem: under a mild technical assumption, Procedures 1--3 described above are statistically valid, even accounting for the selection.
\begin{theorem}
Assume the model~\eqref{eqn:expfam} holds and $g\left(x\right)$ is a Schur-concave function. Then:
\begin{enumerate}
\item Procedure 1 has level $\alpha$ conditional on the best population not winning (otherwise an error is impossible).
\item Procedure 2 gives a conservative $1-\alpha$ lower confidence bound for $\theta_{[1]} - \max_{j \ne [1]} \theta_{j}$.
\item Procedure 3 is a conservative step-down procedure with familywise error rate (FWER) no larger than $\alpha$.
\end{enumerate}
\label{thm:main}
\end{theorem}
\WFcomment{You seem to restate each part of this theorem later in the paper, so that e.g. Theorem 4 is the same as part 1 of Theorem 1.}

@@

\begin{lemma}
\begin{enumerate}
\item Suppose $\left(x_1, x_2, x_3, \ldots\right)$ and $\left(x_1, x_2', x_3' \ldots\right)$ are two vectors in $\RR^n$. Then
$$\left(x_1, x_2, x_3, \ldots\right) \succeq \left(x_1, x_2', x_3', \ldots\right) \text{ if and only if } \left(x_2, x_3, \ldots\right) \succeq \left(x_2', x_3', \ldots\right).$$
\item (Principle of transfer) If $x_1 > x_2$ and $t \ge 0$, then
$$\left(x_1 + t, x_2, x_3, \ldots\right) \succeq \left(x_1, x_2 + t, x_3, \ldots\right).$$
If the $t \le 0$, the majorization is reversed.
\end{enumerate}
\label{lma:twoprop}
\end{lemma}

@@

\item Competitive sports under the Bradley--Terry model. Suppose $n$ players compete in a round robin tournament, where player $j$ has ability $\theta_j$, and the probability of player $j$ winning against player $k$ is
$$\frac{e^{\theta_j - \theta_k}}{1 + e^{\theta_j - \theta_k}} = \frac{e^{\left(\theta_j - \theta_k\right) / 2}}{e^{\left(\theta_j - \theta_k\right) / 2} + e^{\left(\theta_k - \theta_j\right) / 2}}.$$

Let $Y_{jk}$ be an indicator for the match between player $j$ and $k$, where we take $Y_{jk} = 1$ if $j$ beats $k$ and $Y_{jk} = 0$ if $k$ beats $j$. For symmetry, we will also adopt the convention that $Y_{jk} + Y_{kj} = 1$. Thus the joint distribution of $Y=\left(Y_{jk}\right)_{j\neq k}$ is
$$p\left(y\right) \propto \exp\left(\sum_j 2\theta_j \sum_{k \ne j} y_{jk}\right)  = \exp\left(2\theta' x\right),$$
where $x_j = \sum_{k \ne j} y_{jk}$. In other words, if $X_j$ is the number of wins by player $j$, then $X=(X_1,\ldots,X_n)$ is a sufficient statistic with distribution
$$p\left(x\right) = \exp\left(2\theta' x\right) g\left(x\right),$$
where $g\left(x\right)$ is a function that counts the number of possible tournament results giving the net win vector $x$. A bijection proof shows that $x$ is indeed Schur-concave. \WFcomment{What is a bijection proof?} Therefore, we can use Procedures 1--3 to compare player qualities.

\item Comparing the variances of different normal populations. Suppose there are $n$ normal populations with laws $N\left(\mu_j, \sigma_j^2\right)$ and $m$ independent observations from each of them. The sample variance for population $j$ can be denoted as $R_j$. By Cochran's theorem, $\left(m-1\right) R_j \sim \sigma_j^2 \chi_{m-1}^2$, and thus the joint distribution of $R$ is
\begin{align*}
r & \sim \prod_{j=1}^n \left(\frac{\left(m-1\right) r_j}{\sigma_j^2}\right)^{\left(m-3\right) / 2} e^{-\left(m-1\right) r_j / 2 \sigma_j^2} 1_{\left\{r_j > 0 \right\}} \\
& \propto \exp\left(-\frac{m-1}{2 \sigma_1^2} r_1 - \cdots - \frac{m-1}{2 \sigma_n^2} r_n\right) \prod_{j=1}^n r_j^{\left(m-3\right) / 2} 1_{\left\{r > 0\right\}}.
\end{align*}
The carrier measure is $\prod_{j=1}^n r_j^{\left(m-3\right) / 2} 1_{\left\{r > 0\right\}}$, which is Schur-concave. Thus, we can use Procedures 1--3 to find populations with the smallest or largest variances.
\end{enumerate}

@@

\begin{proof}
\WFcomment{I don't think this is a new result. In particular, it's a special case of the partial conjunction null test, but it should also predate that paper.\\

Careful on terminology: the term ``exact'' usually means ``non-asymptotic'' as opposed to ``exactly uniform.'' Also, I was thrown at first when you said ``since $p_j$ are all valid $p$-values.'' I know what you mean now but at first I thought you were saying all the null hypotheses were true.}

Since $p_j$ are all valid $p$-values,
$$\PP_{H_{0j}}\left(p_j < \alpha\right) \le \alpha.$$
So for the union null hypothesis
$$\PP_{H_0}\left(p_* < \alpha\right) = \max_j \PP_{H_{0j}}\left(p_* < \alpha\right) \le \max_j \PP_{H_{0j}}\left(p_j < \alpha\right) \le \alpha.$$
And thus $p_*$ is a valid $p$-value for the union null hypothesis. Now if $p_j$ are all exact, then equality holds above and $p_*$ is exact as well.

\WFcomment{What is $\PP_{H_{0j}}\left(p_* < \alpha\right)$? That is not a well-defined probability because it depends on the distribution of the other p-values (I suppose the same could be said for $\PP_{H_{0j}}(p_j < \alpha)$, but at least that won't confuse anyone). Anyway, the second claim in this Lemma isn't true: if all the p-values are uniform, then the max p-value is not uniform.}
\end{proof}

@@

\begin{theorem}
Assume the model~\eqref{eqn:expfam} holds and $g\left(x\right)$ is a Schur-concave function. Procedure 1 (the unadjusted pairwise test) has level $\alpha$ conditional on the best population not winning.
\label{thm:seltest}
\end{theorem}
\WFcomment{This is just a restatement of conclusion 1 of Theorem 1, right?}

\begin{proof}
\WFcomment{I've now read this proof carefully and it looks generally correct, but I wonder if we could organize it a little more clearly?}

Without loss of generality, otherwise by relabeling, we consider only the case where the winner is $1$ and the runner-up is $2$, etc., i.e.\ $X_1 \ge \cdots \ge X_n$\WFcomment{and that ties are broken such that... need to figure out how to say this right. Also, we should be a little more careful how we say ``without loss of generality'' --- sounds like you're saying we can relabel indices after observing the data?}. In this case, we will test the null hypothesis $H_{01}: \theta_1 \le \max_{j > 1} \theta_j$, which is the union of the null hypotheses $H_{01j}: \theta_1 \le \theta_j$ for $j > 1$. For each of these we can construct an exact $p$-value $p_{1j}$. Hence by \Cref{lma:union}, a test based on $p_{1*} = \max_j p_{1j}$ would be exact for $H_{01}$\WFcomment{No; see note. However, because $p_{1*}=p_{12}$ almost surely given $X_1>X_2>\cdots$, $p_{1*}$ actually is conditionally uniform.}. \WFcomment{As we will see, } Procedure 1 will perform an unadjusted pairwise test comparing $X_1$ to $X_2$. Hence it is sufficient to show that $p_{12} = p_{1*}$ and that the test based on $p_{12}$ coincides with the unadjusted pairwise test.

Following the framework in \citet{Fithian:2014ws}, we consider the selection event where the winner is $1$: \WFcomment{Did we already condition on $X_1\ge X_2\ge\cdots\ge X_n$? See prev. comment.}
$$A_1 = \left\{X_1 \ge \max_{j > 1} X_j\right\}.$$
For convenience, we let
$$D_{jk} = \frac{X_j - X_k}{2} ~~~~ \text{ and } ~~~~ M_{jk} = \frac{X_j + X_k}{2}.$$

We start by re-parametrizing to replace $X_1$ and $X_j$ with $D_{1j}$ and $M_{1j}$ \WFcomment{Worth pointing out we now have an exponential family in $D_{1j},M_{1j},\cdots$ with nat. param.s ...?} and consider
\begin{equation}
\mathcal{L}_{\theta_1 - \theta_j = 0} \left(D_{1j} \middle| M_{1j}, X_{\setminus\left\{1, j\right\}}, A_1\right), \text{ where } A_1 = \left\{D_{1j} \ge \max_{k \ne 1, j} X_k - M_{1j}\right\} \cap \left\{D_{1j} \ge 0\right\}.
\label{eqn:condlaw}
\end{equation}
The conditional law in \Cref{eqn:condlaw}, in particular, is a truncated distribution
\begin{align*}
D_{1j} & \sim \exp\left(\left(\theta_1 - \theta_j\right) D_{1j} + \theta_2 X_2 + \cdots + \left(\theta_1 + \theta_j\right) M_{1j} + \cdots + \theta_n X_n \right) \\
& ~~~~~~~~ g\left(M_{ij} + D_{ij}, X_2, \ldots, M_{ij} - D_{ij}, \ldots X_n\right) 1_{A_1} \\
& \sim g\left(M_{ij} + D_{ij}, X_2, \ldots, M_{ij} - D_{ij}, \ldots X_n\right) 1_{A_1}.
\end{align*}
\WFcomment{What happened to the other $\theta_j$ values? I think the first ``$\sim$'' above should be a ``$\propto$'' and you need to say where all the $\theta$'s went.}

@@

By construction, $p_{1j}$ satisfies
$$\PP_{H_{01j}}\left(p_{1j} < \alpha \middle| M_{1j}, X_{\setminus\left\{1, j\right\}}, A_1\right) = \alpha.$$
Taking expectation on both sides gives \WFcomment{``Marginalizing over $M_{1j},X_{\setminus{1,j}}$,'' maybe?}
$$\PP_{H_{01j}}\left(p_{1j} < \alpha \middle| A_1\right) = \alpha.$$
Therefore these $p_{1j}$ are indeed valid exact $p$-values.

Without loss of generality, it is sufficient to show that $p_{12} \ge p_{13}$. In the computation of either $p$-value, $X_4, \ldots, X_n$ are all conditioned on. The first point in \Cref{lma:twoprop} says that we may assume $n = 3$ without affecting the Schur-concavity of $g$. \WFcomment{Again, exactly what are we doing here? I think we're not really assuming $n=3$; more like conditioning on the other variables to reduce to a case where $n=3$, but we need to be explicit about how this reduction works.} This allows us to clean up our notation and
\begin{align*}
p_{12} & = \frac{\int_{D_{12}}^\infty g\left(M_{12} + z, M_{12} - z, X_3\right) \,dz}{\int_0^\infty g\left(M_{12} + z, M_{12} - z, X_3\right) \,dz} \\
p_{13} & = \frac{\int_{D_{13}}^\infty g\left(M_{13} + z, X_2, M_{13} - z\right) \,dz}{\int_{\max\left\{X_2 - M_{13}, 0\right\}}^\infty g\left(M_{13} + z, X_2, M_{13} - z\right) \,dz}
\end{align*}

Suppose $X_2 < M_{13}$. \WFcomment{Changing variables to $z + D_{12}$ and $z + D_{13}$ respectively}, we can re-parametrize the integrals above to give
\begin{align*}
p_{12} & = \frac{\int_0^\infty g\left(X_1 + z, X_2 - z, X_3\right) \,dz}{\int_0^\infty g\left(M_{12} + z, M_{12} - z, X_3\right) \,dz} \\
& = \frac{\int_0^\infty g\left(X_1 + z, X_2 - z, X_3\right) \,dz}{\int_{-D_{12}}^\infty g\left(X_1 + z, X_2 - z, X_3\right) \,dz} \\
p_{13} & = \frac{\int_0^\infty g\left(X_1 + z, X_2, X_3 - z\right) \,dz}{\int_0^\infty g\left(M_{13} + z, X_2, M_{13} - z\right) \,dz} \\
& = \frac{\int_0^\infty g\left(X_1 + z, X_2, X_3 - z\right) \,dz}{\int_{-D_{13}}^\infty g\left(X_1 + z, X_2, X_3 - z\right) \,dz}
\end{align*}
To help see the re-parametrization, each of these integrals can be thought of in terms of integrals along segments and rays. For example $p_{12}$ can be represented in terms of integrals $A$ and $B$ in \Cref{fig:p-value}. Specifically,
$$p_{12} = \frac{B}{A + B}$$

\begin{figure}[htbp]
\begin{center}
\begin{tikzpicture}
	\coordinate (C1) at (60:5);
	\coordinate (C2) at (300:3);
	\coordinate (A) at (60:3);
	\coordinate (B) at ($(A) + (330:3)$);
	\draw[dashed] (0, 0) -- (C1);
	\draw[dashed] (0, 0) -- (C2);
	\fill[mid_green] (0, 0) -- (C1) -- ($(C1) + (7, 0)$) -- ($(C2) + (8, 0)$) -- (C2) -- cycle;
	\node[above left] at ($(C2) + (8, 0)$) {$A_1$};
	\draw[thick] (A) -- (B) node[midway, above right] {$A$};
	\draw[thick, ->] (B) -- ++(330:5) node[midway, above right] {$B$};
	\fill (A) circle(2pt) node[above left] {$\left(M_{12}, M_{12}, X_3\right)$};
	\fill (B) circle(2pt) node[above right] {$\left(X_1, X_2, X_3\right)$};
	\draw[thick, ->] (0, 0) -- (1, 0) node[right] {\tiny $\left(1, 0, 0\right)$};
	\draw[thick, ->] (0, 0) -- (120:1) node[above] {\tiny $\left(0, 1, 0\right)$};
	\draw[thick, ->] (0, 0) -- (240:1) node[below] {\tiny $\left(0, 0, 1\right)$};
\end{tikzpicture}
\end{center}
\caption{The $p$-value $p_{12}$ can be written in terms of integral $A$ along the segment and $B$ along the ray. The diagram is drawn a level set of $x_1 + x_2 + x_3$ \WFcomment{Problem: the point $(1,0,0)$ is not actually in that level set.}. The green region represents the selection event $A_1$.}
\label{fig:p-value}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\begin{tikzpicture}
	\coordinate (C1) at (60:5);
	\coordinate (C2) at (300:3);
	\coordinate (A) at (60:3);
	\coordinate (B) at ($(A) + (330:3)$);
	\coordinate (C) at ($(0, 0)!(B)!(C2)$);
	\coordinate (D) at ($(A) + (150:1)$);
	\draw[dashed] (0, 0) -- (C1);
	\draw[dashed] (0, 0) -- (C2);
	\fill[mid_green] (0, 0) -- (C1) -- ($(C1) + (7, 0)$) -- ($(C2) + (8, 0)$) -- (C2) -- cycle;
	\node[above left] at ($(C2) + (8, 0)$) {$A_1$};
	\draw[thick] (A) -- (B) node[midway, above right] {$A$};
	\draw[thick, ->] (B) -- ++(330:5) node[midway, below left] {$B$};
	\fill (A) circle(2pt) node[above right] {$\left(M_{12}, M_{12}, X_3\right)$};
	\fill (B) circle(2pt) node[right] {$\left(X_1, X_2, X_3\right)$};
	\draw[thick] (C) -- (B) node[midway, below right] {$C$};
	\node[below] at (C) {$\left(M_{13}, X_2, M_{13}\right)$};
	\draw[thick, ->] (B) -- ++(30:5) node[midway, above left] {$D$};
	\fill ($(0, 0)!(B)!(C2)$) circle(2pt);
	\draw[thick, dashed] (A) -- (D) node[midway, below left] {$\tilde{A}$};
	\fill (D) circle(2pt) node[above] {$\left(M_{13}, X_2 + D_{13}, X_3\right)$};
	\draw[thick, dotted] (C) -- (D) node[midway, below, rotate=-90] {$\succeq$};
	\draw[thick, dotted] (A) -- ++(0, -3) node[midway, below, rotate=-90] {$\succeq$};
	\draw[thick, dotted] ($(B) + (30:4)$) -- ($(B) + (330:4)$) node[midway, below, rotate=-90] {$\succeq$};
\end{tikzpicture}
\end{center}
\caption{The $p$-value $p_{12}$ can be written in terms of integral $A$ along the segment and $B$ along the ray; and $p_{13}$ in terms of $C$ and $D$. $A'$ would refer to the sum of $A$ with the dashed line portion labeled as $\tilde{A}$, formally explained in \Cref{eqn:int_extension}. The majorization relation is indicated by the dotted line. \WFcomment{The point $(X_1,X_2,X_3)$ is cut off a bit in the picture.}}
\label{fig:compare_rays}
\end{figure}

@@

For the alternative case where $X_2 \ge M_{13}$, the segment $C$ will reach the line $x_1 = x_2$ first before it reaches $x_1 = x_3$, ending at $\left(X_2, X_2, X_1 - X_2 + X_3\right)$ instead. But we can still extend $A$ by $\tilde{A}$ to $\left(X_2, X_1, X_3\right)$. The rest of the proof follows. In either cases, $p_{12} \ge p_{13}$, or in generality, $p_{12} \ge p_{1j}$ for $j > 1$. In other words, $p_{12} = p_{1*}$.

@@

The proof above holds true if the exponential family is defined on the counting measure. If ties are broken independently and randomly, the end points on the rays can be considered as ``half an atom'' if the coordinates are integers, and a ``full atom'' otherwise. \WFcomment{Should be part of the proof.}

@@

\begin{theorem}
\label{thm:stoch}
$X_1 \ge X_2$ in stochastic order if and only if $\theta_1 > \theta_2$.
\end{theorem}
\WFcomment{Under what conditions? For a multivariate exponential family with a symmetric carrier distribution, right? Also, are we sure this is a new result?}

@@

\subsection{Multinomial Case: Connection with the Subset Selection}
\label{sec:subsetsel}
\WFcomment{Section title can be improved: this section is primarily about a power comparison with the most natural competing procedure.}

\citet{Gupta:1967wg} devises a rule to select a subset that includes the maximum $\pi_j$. In other words, if the selected subset is $J\left(X\right)$, it guarantees
\begin{equation}\label{eq:subsetsel}
\PP\left(\argmax_j \pi_j \in J\left(X\right)\right) \ge 1 - \alpha.
\end{equation}
This is achieved by finding an integer $D$, as a function on $m$, $n$ and $\alpha$, and selecting by
$$J\left(X\right) = \left\{j: X_j \ge \max_k X_k - D\right\}.$$

\WFcomment{Why is $D$ capitalized? It's not a random variable, is it? Also, can you explain how $D$ is selected? e.g., ``Here, we take $d(m,n,\alpha)$ to be the smallest integer such that \eqref{eq:subsetsel} holds for any $\pi$.''}
It also provides the method to choose $D$. The subset selection can be modified. Inherently, the event $\left\{J\left(X\right) = \left\{1\right\}\right\}$ is the same as inferring $\pi_1$ is the largest. We thus implemented their test for this purpose. \WFcomment{The phrasing here is awkward because the relationship between successive sentences is not clear. Instead try something like: ``Subset selection is closely related to testing whether the winner is the best. In particular, we can define a test that declares $j$ the best whenever $\{J(X)=\{j\}\}$. If $J(X)$ satisfies \eqref{eq:subsetsel}, this test is valid at level $\alpha$. We next compare the power of the resulting test against the power of our Procedure 1 in a multinomial example with $pi \propto \left(e^\delta, 1, \ldots, 1\right)$, for several combinations of $m$ and $n$.''}

@@

\WFcomment{Is there any way we can get an asymptotic expression for $d$ in terms of $n$, as $m\to\infty$, and compare it to our procedure's ``effective $d$''? I suspect there is a $\log n$ factor in there that we don't have.}

\WFcomment{``To interpret, e.g., the lower left plot, suppose that in a poll of $m=250$ respondents, one candidate enjoys $20\%$ support and the other $n-1=9$ split the remainder ($\smash{\delta = \log\frac{0.2}{0.8 / 9} \approx 0.69}$). Then our procedure has power XXXX to detect the best candidate, while Gupta \& Nagel's procedure has power YYYY.''}

\section{By How Much?}
\label{sec:confbound}
\WFcomment{I like that your section heading recalls the earlier discussion, but this feels a little informal for a section heading.}
